\bf Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2016-02-04 jasa/paper-jasa.tex
Section 2.3: Juan comments

&= \frac{p_\mathbf{X}(\mathbf{x}|\theta_0)}{p_\mathbf{X}(\mathbf{x}|\theta_1)} \int_{\{\mathbf{x}^\prime \in \mathbb{R}^p : s(\mathbf{x}^\prime) = u\}}  \frac{1}{|\nabla s(\mathbf{x}^\prime)|}  p_\mathbf{X}(\mathbf{x}^\prime|\theta_1) dS_{\mathbf{x}^\prime}.

@@

As outlined above, any consistent probalilistic classification algorithm can be
used for learning an approximate  map $\hat{s}(\mathbf{x})$ of
Eqn.~\ref{eqn:best-s-clf}. In the common case where the density ratio is
expected to smoothly vary around $\mathbf{x}$, we would however recommend
learning models whose output value $\hat{s}(\mathbf{x})$ also smoothly varies
around $\mathbf{x}$, such as neural networks. For small training sets, tree-based
methods are not expected to work so well for this use case, since they usually
model $\hat{s}(\mathbf{x})$ as a non-strictly monotonic composition of step functions.
In particular, in such cases where $s(\mathbf{x})$ is not monotonic with $r(\mathbf{x})$, Jacobian
factors in Eqn.~\ref{eqn:jacob} do not cancel, resulting in a biased
approximation of the density ratio.

>>>>

&= \frac{p_\mathbf{X}(\mathbf{x}|\theta_0)}{p_\mathbf{X}(\mathbf{x}|\theta_1)} \int_{\{\mathbf{x}^\prime \in \mathbb{R}^p : s(\mathbf{x}^\prime) = u\}}  \frac{1}{|\nabla s(\mathbf{x}^\prime)|}  p_\mathbf{X}(\mathbf{x}^\prime|\theta_1) dS_{\mathbf{x}^\prime}. \label{eqn:factorization}

@@

As outlined above, any consistent probalilistic classification algorithm can be
used for learning an approximate  map $\hat{s}(\mathbf{x})$ of
Eqn.~\ref{eqn:best-s-clf}. In the common case where the density ratio is
expected to smoothly vary around $\mathbf{x}$, we would however recommend
learning models whose output value $\hat{s}(\mathbf{x})$ also smoothly varies
around $\mathbf{x}$, such as neural networks. For small training sets, tree-based
methods are not expected to work so well for this use case, since they usually
model $\hat{s}(\mathbf{x})$ as a non-strictly monotonic composition of step functions.
In particular, in such cases where $s(\mathbf{x})$ is not monotonic with $r(\mathbf{x})$,
the induced probability does not factorize as in Eqn.~\ref{eqn:factorization}, resulting in a biased 
approximation of the density ratio.
